Hybrid platforms and bargaining

### 2023-04-16 src/presentation/topics_talk.qmd
Add motivation

>>>>

## Motivation

::: {.highlight-block}
Examine the bargaining power implications of hybrid platforms and its welfare consequences
:::

::: {.fragment}
 - Hybrid platform
    - Getting more and more common
    - Seemingly obvious concerns and high-profire competition policy cases
    - Comparatively little reserach
:::
::: {.fragment}
 - Bargaining between participants is rather overlooked in platform settings
   - Most papers assume take-it-or-leave-it offers
:::

::: {.notes}

:::

## Main ideas

 - Use the Shapley-value instead of an extensive-form bargaining model
    - Analytically more tractable
    - Has bargaining interpretation [e.g. @hart1996bargaining; @gul1989bargaining]
    - Has precedents in the IO literature [e.g. @hart1990property; @montez2007downstream]
 - Abstract away from all frictions
    - Allows me to focus on the bargaining channel
    - Offers a good benchmark model
 - Focus on continuum of small players case for tractability
    - Good approximation of the finite player case even for not too many players
    - Results have a nice geometric interpretation

## References

::: {#refs}
:::
